# Spatial Regression
## Library
```{r}
# install.packages("spdep")
# install.packages("spatialreg")
# install.packages("RColorBrewer")
# install.packages("splm")
# install.packages("sf")
# install.packages("ggplot2")
library(spdep)
library(spatialreg)
library(RColorBrewer)
library(splm)
library(sf)
library(ggplot2)
```
## Cross-Section
```{r}
library(readxl)
provinsi <- read_excel("Data/Bab6/provinsi Indonesia.xlsx")
head(provinsi)
```
### OLS Model
```{r}
model1 = log(pdrb) ~ log(investment) + log(infra) + log(revenue)
ols = lm(model1, data=provinsi)
summary(ols)
```

### Weight Matrix
```{r}
migrasi <- read_excel("Data/Bab6/matriks migrasi.xlsx", sheet = 2, col_names = FALSE)
migrasi = as.matrix(migrasi)
W.migrasi = mat2listw(migrasi)
```

### Moran Test and Plot
```{r}
moran.lm = lm.morantest(ols, W.migrasi)
moran.lm
moran.plot(ols$residuals, W.migrasi)
```

### LM Test

```{r}
LM = lm.LMtests(ols, W.migrasi, test="all")
LM
```

### SAR Model
```{r}
sar.provinsi = lagsarlm(model1, data=provinsi, W.migrasi)
summary(sar.provinsi)
```

### Impacts (Spillover)

```{r}
impacts(sar.provinsi, listw=W.migrasi)
```

### SEM Model

```{r}
sem.provinsi = errorsarlm(model1, data=provinsi, W.migrasi)
summary(sem.provinsi)
```

## Spatial Panel
```{r}
library(readxl)
paneljateng <- read_excel("Data/Bab6/panel jateng.xlsx")
head(paneljateng)
```

### Static Panel Regression

```{r}
library(plm)
modelpanel = log(PDRB) ~ log(AK) + log(PAD) + log(UMK) + log(IPM)
fem1 = plm(modelpanel, data=paneljateng, index=c("Region", "Tahun"), model="within")
rem1 = plm(modelpanel, data=paneljateng, index=c("Region", "Tahun"), model="random")
phtest(fem1, rem1)
```

```{r}
library(lmtest)
bptest(fem1)
pbgtest(fem1)
```

### Depndency Test

```{r}
pcdtest(fem1, test="lm")
pcdtest(fem1, test="cd")
```

### Maps Visualization 
```{r}
jateng.map = st_read('Data/Bab6/peta jateng/Jawa_Tengah.shp')
```


```{r}
jateng2011 = subset(paneljateng,(Tahun==2011))
jateng2011 = merge(jateng.map, jateng2011, by.x="KABKOTNO", by.y="NO")
jateng2011 <- st_make_valid(jateng2011)
ggplot(jateng2011) +
  geom_sf(aes(fill = PDRB)) +
  scale_fill_gradientn(colours = brewer.pal(5, "Blues"),
                       values = scales::rescale(seq(min(jateng2011$PDRB), 
                                                    max(jateng2011$PDRB)*1.01, 
                                                    length = 6))) +
  theme_minimal() +
  labs(fill = "PDRB")
```

```{r}
ggplot(jateng2011) +
  geom_sf(aes(fill = IPM)) +
  scale_fill_gradientn(colours = brewer.pal(5, "Greens"),
                       values = scales::rescale(seq(min(jateng2011$IPM), 
                                                    max(jateng2011$IPM)*1.01, 
                                                    length = 6))) +
  theme_minimal() +
  labs(fill = "IPM")
```

### Function for Spatial Panel Evalutation

```{r}
godf.spml<-function(object, k=2, criterion=c("AIC", "BIC"),  ...){
  s<-summary(object)
  l<-s$logLik
  np<- length(coef(s))
  N<- nrow(s$model)
  if(criterion=="AIC"){
    aic<- -2*l+k*np
    names(aic)<-"AIC"
    return(aic)
  }
  if(criterion=="BIC"){
    bic<- -2*l+log(N)*np
    names(bic)<-"BIC"
    if(k!=2){
      warning("parameter <k> not used for BIC")
    }
    return(bic)
  }
}
```

### Spatial Panel Model with Contiguity Weight Matrix

```{r}
jateng.map <- st_make_valid(jateng.map)
listqueen = poly2nb(jateng.map, queen=TRUE)
W.queen = nb2listw(listqueen, style="W")
W.queen
```

```{r}
# SAR Model
sar.fem.contig = spml(modelpanel, data=paneljateng, listw=W.queen, model="within", lag=TRUE, spatial.error="none")
sar.rem.contig = spml(modelpanel, data=paneljateng, listw=W.queen, model="random", lag=TRUE, spatial.error="none")
sphtest(sar.fem.contig, sar.rem.contig)
godf.spml(sar.rem.contig, criterion="AIC")
```

```{r}
# SEM Model
sem.fem.contig = spml(modelpanel, data=paneljateng, listw=W.queen, model="within", lag=FALSE, spatial.error="b")
sem.rem.contig = spml(modelpanel, data=paneljateng, listw=W.queen, model="random", lag=FALSE, spatial.error="b")
sphtest(sem.fem.contig, sem.rem.contig)
godf.spml(sem.rem.contig, criterion="AIC")
```


### Spatial Panel Model with KNN Weight Matrix
```{r}
# K-nearest neighbour with 5 neighbour 
centroids <- st_centroid(jateng.map)
coords <- st_coordinates(centroids)
neighbour = knearneigh(coords, k=5, longlat=T) 
neighbourlist = knn2nb(neighbour)                              
mat.knn5 = nb2mat(neighbourlist, style="W")                     
W.knn5 = nb2listw(neighbourlist, style="W")
W.knn5
```

```{r}
# SAR Model
sar.fem.5nn = spml(modelpanel, data=paneljateng, listw=W.knn5, model="within", lag=TRUE, spatial.error="none")
sar.rem.5nn = spml(modelpanel, data=paneljateng, listw=W.knn5, model="random", lag=TRUE, spatial.error="none")
sphtest(sar.fem.5nn, sar.rem.5nn)
godf.spml(sar.rem.5nn, criterion="AIC")

# SEM Model
sem.fem.5nn = spml(modelpanel, data=paneljateng, listw=W.knn5, model="within", lag=FALSE, spatial.error="b")
sem.rem.5nn = spml(modelpanel, data=paneljateng, listw=W.knn5, model="random", lag=FALSE, spatial.error="b")
sphtest(sem.fem.5nn, sem.rem.5nn)
godf.spml(sem.rem.5nn, criterion="AIC")
```

### Best Model
```{r}
summary(sar.rem.5nn)
```

### Impacts (Spillovr) - Only for SAR Model
```{r}
# Direct and Indirect Effect
time = length(unique(paneljateng$Tahun))
sW.5knn = kronecker(Diagonal(time), listw2dgCMatrix(W.knn5))
set.seed(12345)
trMatc = trW(sW.5knn, type="mult")
imp = impacts(sar.rem.5nn, tr = trMatc, R = 200)
summary(imp, zstats=TRUE, short=T)
```

