# Time Series Spillover - GVAR
## Library
```{r,warning=FALSE}
library(Spillover)
library(vars)
library(urca)
library(splitstackshape)
library(igraph)
library(reshape)
```

## Data: Diebold-Yilmaz 2012

```{r}
data(dy2012)
head(dy2012)  # in log volatility form
```

**log volatility return:** 
$$
\sigma^2_{it} = 0.361[ln(P^{max}_{i,t}) - ln(P^{min}_{i,t-1}))]^2
$$

$$
\sigma_{it} = 100*(\sqrt{252*\sigma^2_{it}})
$$


```{r}
class(dy2012)
```

```{r}
nrow(dy2012)
```

## VAR Model

```{r}
PP.test(dy2012$Stocks)
PP.test(dy2012$Bonds)
PP.test(dy2012$Commodities)
PP.test(dy2012$FX)
```

```{r}
# Optimum Lag
VARselect(dy2012[,-1], lag.max = 4, type = c("both"))
```

```{r}
# VAR Model
VAR_4 <- VAR(dy2012[,-1], p=4)
VAR_4
```

## Volatility Spillover DY-2012

```{r}
# Total Spillover Index
sp <- G.spillover(VAR_4, n.ahead = 10, standardized = F )
sp
```

The total volatility spillover appears in the lower right corner of Table, which indicates that, on average, across our entire sample, 12.6% of the volatility forecast error variance in all four markets comes from spillovers


```{r}
Spillover::net(sp)
```

## Dynamic Spillover Index / rolling-sample total volatility spillover

```{r}
# Data Setting
data(dy2012)
dy2012$Date <- as.Date(dy2012$Date, "%Y-%m-%d")
dy2012 <- as.zoo(dy2012[,-1], order.by = dy2012$Date)
class(dy2012)
```

```{r}
# Generalized rolling spillover index based on a VAR(4)
G_index<- total.dynamic.spillover(dy2012, width = 200, index="generalized", p=4) 
head(G_index, n=10)
```

```{r}
plot(G_index)
```

## Directional volatility spillovers

```{r}
library(zoo)
data(dy2012) # re-import data
class(dy2012)
```

```{r}
dy_results <- dynamic.spillover(dy2012, width=200, remove.own = FALSE)
str(dy_results)
```

```{r}
# Directional volatility spillovers, FROM four asset classes.
pp_from <- plotdy(dy_results, direction = "from")
```

```{r}
# Directional volatility spillovers, TO four asset classes.
pp_to <- plotdy(dy_results, direction = "to")
```

```{r}
# Net volatility spillovers, four asset classes
pp_net <- plotdy(dy_results, direction = "net")
```


```{r}
# Net pairwise volatility spillovers
pp_netpairwise <- plotdy(dy_results, direction = "net_pairwise")
```

```{r}
pp_from_to_pairwise <- plotdy(dy_results, direction = "from_to_pairwise")
```

## Connectedness Network

```{r}
sp <- G.spillover(VAR_4, n.ahead = 10, standardized = F )
datanet <-  Spillover::net(sp)
datanet
```

```{r}
# Data frame node
node_df <- data.frame(rownames(datanet), rownames(datanet),datanet$Net)
names(node_df) <- c("id","label","size")
head(node_df)
```

```{r}
sp <- sp[1:4,1:4]
sp
```

```{r, warning=FALSE}
# Data frame edge
m1 <- melt(sp)[melt(upper.tri(sp))$value,] # FROM
m2 <- melt(sp)[melt(lower.tri(sp))$value,] # TO
m1 <- m1[order(m1$X1),]
m2 <- m2[order(m2$X2),]
```

```{r}
edge_df <- data.frame("to"=m1[,2],"from"=m1[,1], "weight" = m1$value-m2$value)
library(dplyr)
edge_df_positive <- edge_df %>% filter(weight >= 0)
edge_df_negative <- edge_df %>% filter(weight < 0)

edge_df_negative <- edge_df_negative %>%
  mutate(weight = -weight) %>%
  dplyr::rename(to = from, from = to)
edge_df <- bind_rows(edge_df_positive, edge_df_negative)
```

```{r}
positive_weight <- edge_df$weight[edge_df$weight > 0]
negative_weight <- edge_df$weight[edge_df$weight < 0]
positive_size <- node_df$size[node_df$size > 0]
negative_size <- node_df$size[node_df$size < 0]

library(RColorBrewer)
Transmitter_color <- "#2ca25f"
else_color <- "#de2d26"
color_vec1 <- ifelse(edge_df$weight > 0, Transmitter_color, else_color)
color_vec2 <- ifelse(node_df$size > 0, Transmitter_color, else_color)
```

```{r}
graph <- graph_from_data_frame(edge_df, directed = TRUE, vertices = node_df)
E(graph)$color <- "black" # Egde
V(graph)$color <- color_vec2 # Node
E(graph)$weight <- abs(edge_df$weight)
V(graph)$size <- abs(node_df$size)
```


```{r}
E(graph)$weight <- E(graph)$weight / max(E(graph)$weight) * 2
V(graph)$size <- V(graph)$size / max(V(graph)$size) * 50
```

```{r}
plot(graph, edge.width = E(graph)$weight, layout=layout_in_circle(graph), edge.arrow.mode=2, edge.arrow.size=0.2)
```
